The Efficient Handling of Guards in the Design of RPython's Tracing JIT

### 2012-08-14 talk/vmil2012/paper.tex
Rephrase
Mention Armin's hint about continulet-jit-2

For the different benchmarks the backend map has a size of
about 15\% to 20\% of the amount of memory compared to the size of the
generated machine code. On the other hand the generated machine code has only a
size ranging from 20.5\% to 37.98\% of the size of the resume data and the backend map
combined and being compressed as described before.

@@

Based on the observation that guard failure is rare it
would be worth exploring if a more aggressive compression scheme for guards
would be worth the memory saving in contrast to the increased decoding
overhead. Based on the same observation we would like to explore the concept of
LuaJIT's sparse snapshots and its applicability to PyPy.

>>>>

For the different benchmarks the backend map has
about 15\% to 20\% of the size compared to the size of the
generated machine code. On the other hand the generated machine code has only a
size ranging from 20.5\% to 37.98\% of the size of the resume data and the backend map
combined and being compressed as described before.

@@

Based on the observation that guard failure is rare it
would be worth exploring if a more aggressive compression scheme for guards
would be worth the memory saving in contrast to the increased decoding
overhead. Based on the same observation we would like to explore the concept of
LuaJIT's sparse snapshots and its applicability to RPython's JIT.
There is an ongoing effort to replace the backend map in RPython's JIT with a
simpler technique that does not require decoding the backend map on each guard
failure.
